Xor-Some Preregistered Study: Preprocessing

### 2021-10-22 analysis/01_xor-some_prereg_preprocessing_N18.Rmd
add preprocessing of first N18

First, the data is loaded.
```{r, echo=FALSE}
d <- read_csv("./../../data/results_test.csv") #prereg_final

# for testing purposes
d <- d %>% mutate(submission_id = 42)

@@

@@

Exclude participants based on example trials, comprehension question performance, and response patterns.
Participants who gave all responses within the range of 10 and participants who failed more than 0.2 of the comprehension questions are excluded from analysis. 
Participants who failed all example trials are excluded, as well. 
```{r exclusions}
# get participants failing example trials
d_exmpl_fail <- d_exmpl %>% group_by(submission_id) %>% 
  mutate(example_condition = ifelse(grepl("as certainly true", question), "true", 
                                    ifelse(grepl("as certainly false", question), "false",
                                           "uncertain")),
         passed_example_trial = case_when(example_condition == "true" ~ response >= 80,
                                    example_condition == "false" ~ response <= 20,
                                    example_condition == "uncertain" ~ response >= 30),
       #  check if all trials passed
         passed_example = case_when(sum(passed_example_trial) == 0 ~ FALSE,
                                    TRUE ~ TRUE)
         ) %>% filter(passed_example == F)

@@

Write out data for plotting:
```{r}
d_test %>% write_csv("./../../results_prereg_raw_test.csv")
```

@@

Write out tidy data:
```{r}
d_full_clean %>% write_csv("./../../data/results_prereg_tidy.csv")
```

@@

Write out z-scored data
```{r}
d_critical_zScored %>% write_csv("./../../data/results_prereg_tidy_zScored_long.csv")
d_critical_zScored_wide %>% write_csv("./../../data/results_prereg_tidy_zScored_wide.csv")
```

>>>>

First, the data is loaded.
```{r, echo=FALSE}
d <- read_csv("./../data/main/results_73_xor-some-Prolific-main_N18_anonym.csv")

@@

```{r}
# check the distribution of completion times
d_native_completed %>% 
  ggplot(., aes(x=timeSpent)) +
  geom_density()
```

@@

Exclude participants based on example trials, comprehension question performance, and response patterns.
Participants who gave all responses within the range of 10 and participants who failed more than 0.2 of the comprehension questions are excluded from analysis. 
Participants who failed all example trials are excluded, as well.

```{r exclusions}
# get participants failing example trials
d_exmpl_fail <- d_exmpl %>% group_by(submission_id) %>% 
  mutate(example_condition = ifelse(grepl("as certainly true", question), "true", 
                                    ifelse(grepl("as certainly false", question), "false",
                                           "uncertain")),
         passed_example_trial = case_when(example_condition == "true" ~ response >= 80,
                                    example_condition == "false" ~ response <= 20,
                                    example_condition == "uncertain" ~ response >= 30),
       #  check if all trials passed
         passed_example = case_when(sum(passed_example_trial) == 0 ~ FALSE,
                                    TRUE ~ TRUE)
         ) %>% filter(passed_example == F)

@@

Write out data for plotting:
```{r}
d_test %>% write_csv("./../data/main/results_prereg_raw_N18_test.csv")
```

@@

Write out tidy data:
```{r}
d_full_clean %>% write_csv("./../data/main/results_prereg_N18_tidy.csv")
```

@@

Write out z-scored data
```{r}
d_critical_zScored %>% write_csv("./../data/main/results_prereg_tidy_N18_zScored_long.csv")
d_critical_zScored_wide %>% write_csv("./../data/main/results_prereg_tidy_N18_zScored_wide.csv")
```
